%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is a sample header for a sample dissertation. Fill in the name,
% and the other information. LaTeX will work out the table of
% content, the list of figures and of tables for you.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage
\thispagestyle{empty}
% ******* Title page *******
% **************************

\vspace*{2cm}
\begin{center}
{\Large\bf Applicability of complex-valued convolutional neural networks to complex-valued data classification\\} \vspace{2cm} {\large
Omair Khalid\\
\vspace{2cm}
School of Engineering and Physical Sciences \\
Heriot-Watt University\\
\vspace{2cm}
Supervised by: \\
\centering Prof. Andrew Wallace
}

\end{center}

\vspace{5cm}
\begin{center}
{\large A Thesis Submitted for the Degree of \\MSc Erasmus Mundus
in Vision and Robotics (VIBOT) \\\vspace{0.3cm} $\cdot$ 2018
$\cdot$}
\end{center}
\singlespacing


%ABSTRACT
\begin{abstract}
Complex number system ($\mathbb{C}$), a natural extension of Real number system ($\mathbb{R}$), is used to describe many natural phenomena: wind (speed and direction), electromagnetic waves, fMRI data etc. Complex-valued neural networks ($\mathbb{C}$-NNs), a variant of real-valued neural networks that incorporates operations related to complex numbers, aim to exploit richer representational capacity of complex-valued data and have been demonstrated to outperform Real-valued Neural Networks $\mathbb{R}$-NNs at the tasks where the input data is complex in nature e.g. music transcription, speech spectrum prediction etc. However, the recent advancements in deep learning literature, especially regarding real-valued convolutional neural networks (CNNs) and its improvements, have not seen much overlap with $\mathbb{C}$-NNs, and has been dominated mostly by real number representations. If we are to exploit the recent advancements and complex-natured data, CNNs should be able to incorporate processes suited for complex numbers with the recent techniques. We call such CNNs as Complex-valued Convolutional Neural Networks $\mathbb{C}$-CNNs. 

%The design of $\mathbb{C}$-CNNs comes with its own set of challenges.
In this work, we explore if $\mathbb{C}$-CNNs can better exploit information from complex-valued data source as compared to Real-valued CNNs ($\mathbb{R}$-CNNs) to solve a classification problem. We explore the design choices and challenges associated with $\mathbb{C}$-CNNs in particular, and propose two comparable architectures of $\mathbb{C}$-CNN and $\mathbb{R}$-CNNs. We test them on a toy dataset (MNIST+P) and on two real-world radar datasets (Radar-150 and Radar-300). Our results, although inconclusive, suggest comparable performance of $\mathbb{C}$-CNNs and $\mathbb{R}$-CNNs. We further detail future work to validate our results. 

\vspace*{5cm}
\end{abstract}

%QUOTE
\begin{quote}
\vspace*{\fill}
\begin{center}
\begin{quote}
\centering \it The only way out is through.
\end{quote}
\end{center}
\hfill{\small Robert Frost}
\vspace*{\fill}

\end{quote}


\doublespacing

%\pagestyle{empty}
\pagenumbering{roman}
\setcounter{page}{1} \pagestyle{plain}


\tableofcontents

\listoffigures
\listoftables

\chapter*{Acknowledgments}
\addcontentsline{toc}{chapter}
         {\protect\numberline{Acknowledgments\hspace{-96pt}}}
\begin{itemize}
\item[--] God. 
\item[--] Parents, the big sibling, and the little sibling.
\item[--] Prof. Andrew Wallace, \textit{for the opportunity and supervision}. 
\item [--] Marcel Sheeny de Moraes, \textit{for the helpful guidance throughout the journey}.
\item[--] Vision Lab-mates without Clear Vision: Shubham, Alpha, Zaal, and Ziyang, \textit{for the camaraderie}.  
\item[--] Saptarshi, \textit{for generosity in the tough times}.
\item[--] Christina Kuhl and Ahmed Riaz Khan, \textit{for the endless supply of positivity}. 
\item[--] Myself, \textit{for getting it done}.
\end{itemize}

\pagestyle{fancy}